%% The MIT License (MIT)
%%
%% Copyright (c) 2016 Vasil Taneski
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

\documentclass[]{mcdowellcv}
\usepackage{amsmath}

\usepackage[obeyspaces]{url}
\urlstyle{same}
\DeclareUrlCommand\email{\urlstyle{rm}}

\usepackage{hyperref}
\hypersetup{
    %pdftex=true,
    plainpages=false,
    %bookmarks=true,
    %colorlinks=true,
    baseurl={https://vasil.taneski.com/cv},
    bookmarksnumbered=true,
    %backref=true,
    %pagebackref=true,
    %linkcolor=blue,
    %urlcolor=blue,
    %citecolor=black,
    pdfborder=0 0 0,
    pdfhighlight=/P,
    pdftitle={Vasil Taneski},
    pdfsubject={Curriculum Vitae},
    pdfauthor={Taneski, Vasil},
    pdfkeywords={Vasil Taneski, CV, Curriculum Vitae, Resume}
}

\name{Vasil Taneski}
\address{93/9 Ilinden Blvd. \linebreak 1000 Skopje \linebreak Macedonia}
\contacts{+38975290350 \linebreak \email{vasil@taneski.com} \linebreak \url{https://vasil.taneski.com}}

\begin{document}

    % Contact Header
    \pdfbookmark[1]{Contact}{Contact}
    \makeheader
    \label{Contact}

    % Summary
    \pdfbookmark[1]{Summary}{Summary}
    \begin{cvsection}{Summary}
        \label{Summary}
        \begin{cvsubsection}{}{}{}
            I am Senior Developer with more than 10 years of experience, among which a Technical/team Lead and Project Manager with direct control over the entire project and development life-cycle, from long-term planning to short-term activities (initiating, planning, executing, monitoring/controlling and closing the project).\\
            \textit{Specialties:} Python/JavaScript/Ruby/Java Programming, Project Management.
        \end{cvsubsection}
    \end{cvsection}

    % Experience
    \pdfbookmark[1]{Experience}{Experience}
    \begin{cvsection}{Experience}
    \label{Employment Record}
        \begin{cvsubsection}{Senior Software Engineer}{Vox Teneo Macedonia}{Nov. 2014 -- present}
            I am Java/JavaScript Tech. Lead and Python Developer.
            \begin{itemize}
                \item \textit{GesBVD} --- Information system for tracking the health statuses of the animals in Belgium;
                \item \textit{Leveltest} --- Internal application for language assessment;
                \item \textit{Exercise Editors} --- Editors as Angular directives (Bower components) for building language exercises.
            \end{itemize}
        \end{cvsubsection}
        \begin{cvsubsection}{R\&D Engineer}{Digital Medialab}{Nov. 2013 -- Jun. 2014}
            Research and implementation of new digital media opportunities.
            \begin{itemize}
                \item \textit{Coca--Cola 2014 Game} --- Logics and reporting for SMS award game;
                \item \textit{LandrovalPy} --- Realtime messenger API service for thousands of concurrent users;
                % \item xPrint Web Viewer --- Preprint page previewer amd organizer;
                \item \textit{EmbLoop} --- Embedded images sharing application for Intel Edison device.
            \end{itemize}
        \end{cvsubsection}
        \begin{cvsubsection}{Co-Founder \& CTO}{Innologica}{Mar. 2012 -- Jul. 2014}
            As a Technical Officer I was responsible for the work of the Business analyst, Development and Test Teams.\linebreak
            I have lead the development process in the Python, JavaScript, HTML environments.\\
            % My key responsibilities were:
            % \begin{itemize}
            %     \item Managing the software development lifecycle from end to end and code reviewing.
            %     \item Being accountable for the design, development, implementation, maintenance, delivery and improvement of the provided services and products;
            %     \item Defining and communicating the technical vision and delivery strategy, including selecting suitable technologies and making build vs. buy and staffing decisions.
            %     \item Identifying and implementing emerging technologies and engineering practices that will improve efficiency and productivity;
            % \end{itemize}
        \end{cvsubsection}
        \begin{cvsubsection}{Senior Software Engineer}{Seavus}{Feb. 2010 -- Feb.2012}
            I was Senior Python developer with focus on game development (Game design, system architecture and programming).
            % I had direct experience with the whole application development cycle from building project characteristics according to gaming market and trends down to design, modeling and development.
            \begin{itemize}
                \item \textit{Cynedom} --- Massive Multiplayer Online Game with iPhone, Android and Facebook clients.
                \item \textit{SunPower Game}  --- Trivia style Facebook game for SunPower;
                \item \textit{Andappstore} --- Preparing BI reports (ad--hoc/standard) on the work of one of the first Android markets.
            \end{itemize}
        \end{cvsubsection}
        \begin{cvsubsection}{Software Engineer}{Netcetera}{Oct. 2008 -- Jan. 2010}
            I have worked on designing and implementation of EE applications based on Java and Ruby.
            \begin{itemize}
                \item \textit{LBA Online Timetable} --- Web application for presenting the timetable of the Liechtensteinian Bus Company;
                \item \textit{Evita} --- Digital Health Dossier as a unique, multilevel data security concept;
                \item \textit{Checklist Manager} --- Internal application for managing templated check-lists/issue-lists.
            \end{itemize}
        \end{cvsubsection}
        \begin{cvsubsection}{Programmer}{Self--employed}{Jun. 2002 -- Sep. 2008}
            Freelance programmer working mainly on Perl and web based projects.
            \begin{itemize}
                \item \textit{Vezilka} --- Software for automatic embroidery patterns generation;
                \item \textit{EmbroidScript} --- PostScript based extension for describing embroidery patterns;
                \item \textit{IT infrastructure} --- Complete web IT infrastructure for cable distribution network provider Kabelnet.
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}

    % Footer on the first page
    \vfill
    \begin{tabu} to 1\textwidth {X[l,m] X[r,m]}
        \textit{page 1 of 2}
    \end{tabu}
    \clearpage

    % Heder on the second page
    \begin{center}
        \begin{tabu} to 1\textwidth {X[l,m] X[c,m] X[r,m]}
            \small{+38975290350} &
            \textbf{\Large\textls[110]{\textsc{Vasil Taneski}}} &
            \small{\email{vasil@taneski.com}} \linebreak
        \end{tabu}
    \end{center}
    \vspace*{20pt}

    % Education
    \pdfbookmark[1]{Education}{Education}
    \begin{cvsection}{Education}
    \label{Education}
        \begin{cvsubsection}{Macedonia}{\mbox{Ss. Cyril and Methodius University}}{Oct. 1999 -- 2004}
            Dropout from Faculty of Mathematics and Natural Sciences
        \end{cvsubsection}
    \end{cvsection}

    % Computer Knowledge
    \pdfbookmark[1]{Computer knowledge}{Computer knowledge}
    \begin{cvsection}{Computer knowledge}
    \label{Computer knowledge}
        \begin{cvsubsection}{}{}{}
            \begin{itemize}
                \item \textbf{OS}: Unix (various linuces);
                \item \textbf{Languages}: Python, JavaScript, Java, Ruby, BASH, SQL, UML;
                \item \textbf{Web}: HTML, CSS, REST, HTTP, XML;
                \item \textbf{Web Frameworks}: Tornado, Flask, Google App Engine, Django, Sinatra, AngularJS\ldots;
                \item \textbf{DBMS}: MySQL, PostgreSQL, SQLite3, Redis, MongoDB;
                \item \textbf{Dev. Methodologies}: RUP, Agile (XP, Scrum);
                \item \textbf{Tools}: Git, SVN, Grunt, Bower, \LaTeX.
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}

    % Languages
    \pdfbookmark[1]{Languages}{Languages}
    \begin{cvsection}{Languages}
    \label{Languages}
        \begin{cvsubsection}{}{}{}
            \begin{itemize}
                \item \textbf{Macedonian:} native speaker;
                \item \textbf{English:} Fluent in reading, writing and speaking.
            \end{itemize}
        \end{cvsubsection}
    \end{cvsection}
    \vfill
    \begin{tabu} to 1\textwidth {X[l,m] X[c,m] X[r,m]}
        \textit{page 2 of 2} &
        \textit{\url{https://vasil.taneski.com/cv}} &
        \textit{10 March 2016}
    \end{tabu}
    \clearpage
\end{document}
